THESIS PROJECT PROPOSAL

### 2019-10-31 project_ashish/paper.tex
Update paper.tex

The production of Higgs boson in association with single top quark is one of the rare Higgs boson production mode. As the top 
quark is the heaviest fundamental particle in the standard model, due to its large mass, the top quark decay before 
hardronization which allow the possibility to reconstruct top quark from its decay products unlike the lighter quarks which 
undergo hardronization and are seen as bundles of particles in detector called jets. The most probable decay of top quark is into 
bottom(b) quark and W boson.

>>>>

The production of Higgs boson in association with single top quark is one of the rare Higgs boson production mode. As the top 
quark is the heaviest fundamental particle in the standard model, due to its large mass, the top quark decay before 
hardronization which allow the possibility to reconstruct top quark from its decay products unlike the lighter quarks which 
undergo hardronization and are seen as bundles of particles in detector called jets. The most probable decay of top quark is into 
bottom(b) quark and W boson. Using b-jet tagging algorithms, the ejt originating from b-quark can be reconstructed to identity 
top quark. In SM, the coupling of the Higgs boson to fermions is proportional to the mass of the fermions. Thus heavy quarks like 
top,bottom and charm couple strongly to Higgs boson which means that out of all known quarks, top quark couple most strongly to 
the Higgs boson. So, it has a large value of Yukawa coupling Y_t. That is why the Yukawa coupling of the top quark with the Higgs 
boson Y_t has lot of importance as any deviation from standard model prediction might give an indication to new physics. There 
are two processes at LHC which will allow us to directly proble the Yukawa coupling between Higgs Boson and top quark which are 
Higgs boson production in association with top quark pair(t\bar{t}tH) via strong interaction and the production of single top 
quark with a Higgs boson(tH).
